\chapter*{}
\begin{abstract}
\doublespacing
The Commute is an electrically supported long board. Because of rising trend of electric mobility, this product is intended for the daily commuter to reach his destination. With an innovative steering device called Magic Glove, the board’s slim design and leight weight, the Commute provides great usability. The Magic Glove uses an AtMega328 microcontroller to convert the movement of a finger, which is measured by an integrated bending strip, into a digital signal and send it to the long board. To reduce the chance of an accident caused by connecting wires, the steering glove communicates wirelessly over a 2.4GHz module. In addition, this connection is used as a theft protection and also prevents the board from rolling away unintentionally. To reach a controlled starting acceleration, the Commute uses a new motor control technology called Field Oriented Control or FOC. With the implementation, the board reclames energy gained from riding downhill. Due to a high performance microcontroller called STM32F3, the very difficult calculations from this technology are handled easily. The Commute also has a charging circuit which charges the internal Lithium Polymer battery simply by attaching the charging cable. To provide a longer battery life, the charging circuit measures the cell voltages and ensures that they stay balanced. The charging state is visualized by three LEDs which represent charging, ready and fully charged. An AtMega328 microcontroller charges the battery, balances the cells and controls the charging current flowing into the cells. With all these technologies, we were able to create an electrically supported long board that is very convinient for commuters as well as for hobby users. The Magic Glove has been tested by our developer and works as expected. It enables a seemingless driving experience without the need of a remote. The implementation of the FOC algorithm isn't ready for use in the long board becuase the torque controller needs more fine tuning. Balancing the battery works as planned but the charging feature has to be implemented in software.

\paragraph*{Keywords:} Electric mobility, Bending Strip, Field Oriented Control, Cell balance, Long board
\end{abstract}
